Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-30 writeups/dissertation/dissertation.tex
foo

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-priorAddSO-crop.pdf}}}
  \caption{Coefficient values for full models for StackOverflow}
  \label{figContextCoeffSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-priorAddSO-crop.pdf}}}
  \caption{Coefficient values for full models for Twitter}
  \label{figContextCoeffT}
\end{figure}

The range of the confidence intervals is much more narrow than the range of the coefficient values between the components of each model.
This shows that the model is not being overfit, as the weights for each component are relatively stable across the different runs.
The weight of the prior relative to the context terms is also fairly consistent across models and across the two sites.
Across the sites, context is a much stronger predictor than past behavior for StackOverflow, but past behavior is more important for Twitter. 
Within a site, both models are consistent in how they favor context or past behavior.
Also, looking at StackOverflow, both models are consistent in weighting the body more than the title, and the title more than the prior term.

>>>>

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-coeffStd-coeffSO-crop.pdf}}}
  \caption{Coefficient values for full models for StackOverflow}
  \label{figContextCoeffSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-coeffStd-coeffT-crop.pdf}}}
  \caption{Coefficient values for full models for Twitter}
  \label{figContextCoeffT}
\end{figure}

Even at these small sample sizes, the range of the confidence intervals is much more narrow than the range of the coefficient values between the components of each model.
This shows that the model is not being overfit, as the weights for each component are relatively stable across the different runs.
The weight of the prior relative to the context terms is also fairly consistent across models and across the two sites.
Across the sites, context is a much stronger predictor than past behavior for StackOverflow, but past behavior is more important for Twitter. 
Within a site, both models are consistent in how they favor context or past behavior.
Also, looking at StackOverflow, both models are consistent in weighting the body more than the title, and the title more than the prior term.
